Compositional equivalences based on Open pNets

### 2020-02-26 2016-Weak-FH-Bisim/WeakBisim.tex
proofs again checked all but a bit fast on the last thms

$\forall p \in [0..(n_1\!+\!n_2\!+\!2)]\,\, Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_p}},  
				{{\Post\,''_p}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
In this equation, and using case 1 above for all $k\in [0\ldots n_1]$ there is a $p\in [0..m_1]$ such that $\alpha_{1p}=\alpha_k$ (following the re-indexing done in the removal of steps where $Q$ does not move), we have $\Pred_{1p}$ contains $ \alpha_{1p}=\beta_{1 p j_0}$. Because $\beta_{1 p j_0}$ only contains variables of $P$ and $\alpha_k$ only variables of $Q$:
\begin{equation*}
\begin{split}
(\alpha_{1p}=\beta_{1pj_0})\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}&\iff
\alpha_{1p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,''_{1j}}
= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,'_{1j}} \\
&\iff\alpha_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post\,''_{j}}= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,'_{1j}} 
\end{split}
\end{equation*}
We can obtain similar equations for $\alpha_{n_1+1}$ related with $\beta_{2 j_0}$ and the  $\alpha_k$ for $k\geq n_1+2$ related with $\beta_{3 p j_0}$ for some $p$. Note that the substitutions are however more complex. 
Overall we obtain (we skip here the details about the three cases 1, 2, and 3 above that all fall into the same equation because of the re-indexing we perform): 
\begin{equation}\label{eqproofbeta}
\Pred_\beta \iff \gamma_{j_0}=
\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,''_{j}}|p\in[0..n_1+n_2+2]]}
\end{equation}

@@

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (they are $\tau$ transitions). By considering the sequence of $\tau$ and non-$\tau$ actions we split the sequence of actions into $n+1$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.

@@

 We can decompose each of the $n+1$ subsequences in the following way (see Figure~\ref{figproof}).
For $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$. For $l\in [1..n]$,  $n'_l$ is any index between $n_{l-1}$ and $n_l$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$. We obtain $n+1$ subsequences  made of the following OTs, for all $k\in [0..n]$ :\\
\begin{small}
$\forall p\! \in\! [n'_{k}..(n_k\!-\!1)] Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{p}}},  
				{{\Post\,''_{p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,\quad
Q\models{\openrule
			{
				\beta_{n_k j}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{n_k}}},  
				{{\Post\,''_{n_k}}}}
				{\ostate{v_{n_kl}^{l\in L_Q}} \OTarrow {\alpha_{{n_k}}}
				\ostate{v_{(n_k+1)l}^{l\in L_Q}}}
				}%\]
$
\end{small}
and\\
\begin{small}
$\forall p \in [(n_k\!+\!1)..(n'_{k+1}\!-\!1)]\,\, Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{p}}},  
				{{\Post\,''_{p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$
\end{small}
\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
				{{\Post_k}}}
			{\ostate{v_{kl}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
				\ostate{(v_{kl}')^{l\in L_Q}}}
		}%\]
\end{mathpar}
$\alpha_k'=\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}}$\\
$\forall l \in L_Q. v_{kl}=v_{(n'_{k})l} \wedge v_{kl}'=v_{(n'_k)l}$\\
$\displaystyle{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=\displaystyle{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}} \dotcup\\
~~\qquad \qquad\qquad\mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
\vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post\,''_{l}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}} }\\
%
\Pred_k=\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\Pred\,''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\\ 
~\qquad\quad\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post\,''_{j}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{j}}
\\
\Post_k= \bigotimes_{j=n'_{k+1}-1}^{n'_{k}}\!\!\Post\,''_{j}$\\

@@

We need now to show that this set of WOT verify the conditions of the lemma, i.e. it is a set of WOT of the form:
\[	Q\models{\openrule
			{
				\gamma_{p j}^{j\in J_p}, \Pred_p,  
				\Post_p}
			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
		}\]
With
\[  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad\text{trivial}\]
\[ \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigotimes_{i=p-1}^{0}\Post_i)}\]
Indeed we have:
\begin{equation*}
\begin{split}
\gamma_j^{j\in J}&=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\! \Post_{1j}}}\dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }\\
\end{split}\end{equation*}

@@

Finally we have:\\

@@

		\Post_p}$\\
Because

@@

\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose1} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
	Suppose $j_0\in J$  and additionally:\\[-2ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\beta_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
		\ostate{(s_i')^{\, i\in L}}}
}
\quad\text{~~and~~}\quad
Q\models{\openrule
	{
		\set{\gamma},
		 \Pred_Q,  
		\Post_Q}
	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
		\ostate{(s'_{i})^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Let 
\begin{mathpar}
%J_Q=\displaystyle{\bigcup_{t=0}^nJ_{t}}
%\qquad
\Pred\,'=\Pred\land (\beta_{j_0}=\alpha_Q\land \Pred_Q) \quad\text{~~and~~}\quad
%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
\Post\,'=\Post\uplus\Post_Q
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\set{\gamma}\uplus\vis{\beta_j^{j\in J\setminus \{j_0\}}}, 
			\Pred\,',  \Post\,'
			 }
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\begin{proof}
By  Lemma \ref{lem-rel-OT-WOT} we can decompose the WOT of $Q$ into  a series of $k+1$ and $k'+1$ tau open transitions and an observable open transition:
\begin{mathpar}
\forall h\!\in\![0..k].Q\models\openrule
    {\set{\beta_{1h}},\Pred_{1h},\Post_{1h}   }
         {\ostate{{(s_{1h})}} \OTarrow {\tau} \ostate{{(s_{1(h+1)})}}}, \quad
Q\models{\openrule
	{
		\set{\beta_2},
		 \Pred_2,  
		\Post_2}
	{\ostate{s_{20}}\OTarrow {\alpha'_Q}
		\ostate{s_{21}}}
}, \\ \quad\text{~~and~~}\quad 
\forall h \in [0..k'].Q\models\openrule
         {
           \set{\beta_{3h}},\Pred_{3h}, \Post_{3h}}
         { \ostate{(s_{3h})} \OTarrow {\tau} \ostate{(s_{3(h+1)})}}
\end{mathpar}
such that\\ 
$\alpha_Q=\alpha'_Q\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$\\
$s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\
\begin{small}
$\displaystyle{
\set{\gamma}=\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{j=h-1}^{0}\!\! \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=k}^{0}\Post_{1j}}} \dotcup}$\\
 $~~\hspace{1.8em}\displaystyle{ \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{j=h-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=k}^{0}\Post_{1j}} }}
\\
\Pred_Q=\bigwedge_{h=0}^{k}\!\big(\Pred_{1h}\subst{\bigotimes_{j=h-1}^{0}\Post_j^1}\big)\land \Pred_2\subst{\bigotimes_{h=k}^{0}\Post_{1h}}\land\\~\qquad\qquad \bigwedge_{h=0}^{k'}\!\Pred_{3h}\subst{\bigotimes_{j=h-1}^{0}{\Post_{3j}}\otimes{\Post_2}  \otimes\bigotimes_{h=k}^{0}\Post_{1h}}
\\
\Post_Q=\bigotimes_{h=k'}^{0}\Post_{3h}\otimes\Post_2\otimes\bigotimes_{j=k}^{0}\Post_{1j}
$
\end{small}
\begin{enumerate}

@@

%
%\[P[Q]_{j_0}\!\models		
%\openrule
%    {
%       {\beta^i_{p j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2},{\Pred_p}\!\!'',{\Post_p}\!\!''   }
%         {\ostate{s^{i\in L \uplus L_Q}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L\uplus L_Q }_{(p+1)i}}}\] \\
% such that  ${\Pred_p}\!\!'' \iff {\Pred_p}
%		\land {\Pred_p}\!\!'\land \alpha_t=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
%		{\Post_p}\!\!'$\\ 
\item We proceed in the same way as the first item for $k'$ last weak open transitions, and we obtain $k'$ open tau transitions.\\
\end{enumerate}

Using Lemma \ref{lem-rel-OT-WOT}, from cases $(1)$, $(2)$ and $(3)$ we get: 
\[P[Q]_{j_0}\!\models		
\openrule
    {
\set{\gamma_c}, \Pred_c,
\Post_c}
         {\ostate{s_{10}\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha'} 
	\ostate{{{s'}^{i\in L}_{i}\uplus s_{3(k'+1)}}}}\] 
where\\
$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$
and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$.\\
$\displaystyle{
\set{\gamma_c}=\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{i=h-1}^{0}\!\! \Post_{1i} } }  \dotcup  \vis{({\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2})\subst{\bigotimes_{i=k}^{0}\Post_{1i}}} \dotcup}$ \\ 
$~~\hspace{1.8em}\displaystyle{\mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{i=h-1}^{0}\!\!\Post_{3i}\shortotimes\Post_2\shortotimes\bigotimes_{i=k}^{0}\Post_{1i}} }}$\\
$~~\hspace{0.6em}=\set{\gamma}\uplus\vis{\beta_j^{\in J\setminus \{j_0\}}} \quad$  because $\Post_{1j}$  does not act on variables of $\beta_j$.  \\
\begin{small}
$\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_{1i}}\land
\left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\\displaystyle
\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigotimes_{i=h-1}^{0}{\Post_{3i}}\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}
\end{array}
$\\
$\Post_c=\displaystyle{(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}$\\
\end{small}
\noindent Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\

>>>>

$\forall p \in [0..(n_1\!+\!n_2\!+\!2)]\,\, Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_p}},  
				{{\Post\,''_p}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
In this equation, and using case 1 above for all $k\in [0\ldots n_1]$ there is a $p\in [0..m_1]$ such that $\alpha_{1p}=\alpha_k$ (following the re-indexing done in the removal of steps where $Q$ does not move), we know that $\Pred_{1p}$ contains the predicate $( \alpha_{1p}=\beta_{1 p j_0})$. Because $\beta_{1 p j_0}$ only contains variables of $P$ and $\alpha_k$ only variables of $Q$, we have:
\begin{equation*}
\begin{split}
(\alpha_{1p}=\beta_{1pj_0})\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}&\iff
\alpha_{1p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,''_{1j}}
= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,'_{1j}} \\
&\iff\alpha_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post\,''_{j}}= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,'_{1j}} 
\end{split}
\end{equation*}
We can obtain similar equations for $\alpha_{n_1+1}$ related with $\beta_{2 j_0}$ and the  $\alpha_k$ for $k\geq n_1+2$ related with $\beta_{3 p j_0}$ for some $p$. Note that the substitutions are however more complex in the other cases. 
Overall we obtain (we skip here the details about the three cases 1, 2, and 3 above that all fall into the same equation because of the re-indexing we perform): 
\begin{equation}\label{eqproofbeta}
\Pred_\beta \iff \gamma_{j_0}=
\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,''_{j}}|p\in[0..n_1+n_2+2]]}
\end{equation}

@@

Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (they are $\tau$ transitions). By considering the sequence of $\tau$ and non-$\tau$ actions we split the sequence of actions into $n+1$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many non-observable ($\tau$) ones.

@@

 We can decompose each of the $n+1$ subsequences in the following way (see Figure~\ref{figproof}).
For $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$. For $l\in [1..n]$,  $n'_l$ is any index between $n_{l-1}$ and $n_l$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$. We obtain $n+1$ subsequences  made of the following OTs, for all $k\in [0..n]$ :\\
\begin{small}
$\forall p\! \in\! [n'_{k}..(n_k\!-\!1)] Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{p}}},  
				{{\Post\,''_{p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
,\quad
Q\models{\openrule
			{
				\beta_{n_k j}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{n_k}}},  
				{{\Post\,''_{n_k}}}}
				{\ostate{v_{n_kl}^{l\in L_Q}} \OTarrow {\alpha_{{n_k}}}
				\ostate{v_{(n_k+1)l}^{l\in L_Q}}}
				}%\]
$
\end{small}
and\\
\begin{small}
$\forall p \in [(n_k\!+\!1)..(n'_{k+1}\!-\!1)]\,\, Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{p}}},  
				{{\Post\,''_{p}}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$
\end{small}
\\ 
Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
\begin{mathpar}
Q\models{\openrule
			{
			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
				{{\Post_k}}}
			{\ostate{v_{kl}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
				\ostate{(v_{kl}')^{l\in L_Q}}}
		}%\]
\end{mathpar}
With:
$\forall l \in L_Q. v_{kl}=v_{(n'_{k})l} \wedge v_{kl}'=v_{(n'_k)l}$\\
$\alpha_k'=\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}}$\\
$\displaystyle{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=\displaystyle{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}} \dotcup\\
{}~~\qquad \qquad\qquad\mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
\vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post\,''_{l}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}} }\\
%
\Pred_k=\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\Pred\,''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\\ 
{}~\qquad\quad\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post\,''_{j}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{j}}
\\
\Post_k= \bigotimes_{j=n'_{k+1}-1}^{n'_{k}}\!\!\Post\,''_{j}$\\

@@

We need now to show that this set of WOT verifies the conditions of the lemma, i.e. it is a set of WOT of the form:
\[	Q\models{\openrule
			{
				\gamma_{p j}^{j\in J_p}, \Pred_p,  
				\Post_p}
			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
		}\]
With
\[  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad\text{trivial}\]
\[ \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigotimes_{i=p-1}^{0}\Post_i)}\]
Indeed we have:
\begin{equation*}
\begin{split}
\gamma_j^{j\in J}=&\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\! \Post_{1j}}}\dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup\\& \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }\\
\end{split}\end{equation*}

@@

Finally we have~~

@@

		\Post_p}$\quad
because

@@

\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose1} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
	Suppose $j_0\in J$  and:\\[-1ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\beta_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
		\ostate{(s_i')^{\, i\in L}}}
}
\quad\text{~~and~~}\quad
Q\models{\openrule
	{
		\set{\gamma},
		 \Pred_Q,  
		\Post_Q}
	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
		\ostate{(s'_{i})^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Let\\[-3ex] 
\begin{mathpar}
%J_Q=\displaystyle{\bigcup_{t=0}^nJ_{t}}
%\qquad
\Pred\,'=\Pred\land (\beta_{j_0}=\alpha_Q\land \Pred_Q) \quad\text{~~and~~}\quad
%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
\Post\,'=\Post\uplus\Post_Q
\end{mathpar}
Then, we have\\[-3ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\set{\gamma}\uplus\vis{\beta_j^{j\in J\setminus \{j_0\}}}, 
			\Pred\,',  \Post\,'
			 }
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\begin{proof}
By  Lemma \ref{lem-rel-OT-WOT} we can decompose the WOT of $Q$ into  a series of $k+1$ and $k'+1$ tau open transitions and an observable open transition:
\begin{mathpar}
\forall h\!\in\![0..k].Q\models\openrule
    {\set{\beta_{1h}},\Pred_{1h},\Post_{1h}   }
         {\ostate{{(s_{1h})}} \OTarrow {\tau} \ostate{{(s_{1(h+1)})}}}, \quad
Q\models{\openrule
	{
		\set{\beta_2},
		 \Pred_2,  
		\Post_2}
	{\ostate{s_{20}}\OTarrow {\alpha'_Q}
		\ostate{s_{21}}}
}, \\ \quad\text{~~and~~}\quad 
\forall h \in [0..k'].Q\models\openrule
         {
           \set{\beta_{3h}},\Pred_{3h}, \Post_{3h}}
         { \ostate{(s_{3h})} \OTarrow {\tau} \ostate{(s_{3(h+1)})}}
\end{mathpar}
such that

\begin{small}
$s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$
\begin{align*}
\alpha_Q=&\alpha'_Q\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}\\
\set{\gamma}=&\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{j=h-1}^{0}\!\! \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=k}^{0}\Post_{1j}}} \dotcup%\\
		%&
 \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{j=h-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=k}^{0}\Post_{1j}} }\\
\Pred_Q=&\bigwedge_{h=0}^{k}\!\big(\Pred_{1h}\subst{\bigotimes_{j=h-1}^{0}\Post_j^1}\big)\land \Pred_2\subst{\bigotimes_{h=k}^{0}\Post_{1h}}\land\\
&		\bigwedge_{h=0}^{k'}\!\Pred_{3h}\subst{\bigotimes_{j=h-1}^{0}{\Post_{3j}}\otimes{\Post_2}  \otimes\bigotimes_{h=k}^{0}\Post_{1h}}\\
\Post_Q=&\bigotimes_{h=k'}^{0}\Post_{3h}\otimes\Post_2\otimes\bigotimes_{j=k}^{0}\Post_{1j}
\end{align*}

\end{small}
\begin{enumerate}

@@

%
%\[P[Q]_{j_0}\!\models		
%\openrule
%    {
%       {\beta^i_{p j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2},{\Pred_p}\!\!'',{\Post_p}\!\!''   }
%         {\ostate{s^{i\in L \uplus L_Q}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L\uplus L_Q }_{(p+1)i}}}\] \\
% such that  ${\Pred_p}\!\!'' \iff {\Pred_p}
%		\land {\Pred_p}\!\!'\land \alpha_t=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
%		{\Post_p}\!\!'$\\ 
\item We proceed in the same way as the first item for $k'$ last weak open transitions, and we obtain $k'$ open tau transitions.
\end{enumerate}

Using Lemma \ref{lem-rel-OT-WOT}, from cases $(1)$, $(2)$ and $(3)$ we get: 
\[P[Q]_{j_0}\!\models		
\openrule
    {
\set{\gamma_c}, \Pred_c,
\Post_c}
         {\ostate{s_{10}\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha'} 
	\ostate{{{s'}^{i\in L}_{i}\uplus s_{3(k'+1)}}}}\] 
where ~~
$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$
and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$.\\
$\displaystyle{
\set{\gamma_c}=\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{i=h-1}^{0}\!\! \Post_{1i} } }  \dotcup  \vis{({\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2})\subst{\bigotimes_{i=k}^{0}\Post_{1i}}} \dotcup}$ \\ 
${}~~\hspace{1.8em}\displaystyle{\mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{i=h-1}^{0}\!\!\Post_{3i}\shortotimes\Post_2\shortotimes\bigotimes_{i=k}^{0}\Post_{1i}} }}$\\
${}~~\hspace{0.6em}=\set{\gamma}\uplus\vis{\beta_j^{\in J\setminus \{j_0\}}} \quad$  because $\Post_{1j}$  does not act on variables of $\beta_j$.  \\
\begin{small}
$\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_{1i}}\land
\left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\\displaystyle
\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigotimes_{i=h-1}^{0}{\Post_{3i}}\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}
\end{array}
$\\
$\Post_c=\displaystyle{(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}$
\end{small}

\noindent Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$

Note also that $\Post$ only acts on variables of $P$ while $\Post_{1i}$ only acts on state variables of $Q$. We conclude on predicate and posts as follows\footnote{$\Post_{1i}$ only has an effect on variables of $Q$ and thus does not modify $\Pred$ or $\beta_{j_0}$}:
\begin{equation*}
\begin{split}
\Pred_c&=\Pred_Q\land\Pred\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land
(\alpha'_Q=\beta_{j_0})\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\\
&=\Pred_Q\land\Pred\land \alpha_Q=\beta_{j_0}\\[.3ex]
\Post_c&=\Post\uplus\Post_Q \\[-3ex]
\end{split}
\end{equation*}
\end{proof}
